Fast Hyperparameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2017-02-08 paper.tex
6 pages again!

\usepackage{listings}
\lstset{
	language=Python,
	basicstyle=\footnotesize,
	commentstyle=\color{mygreen},
	frame=single,
	keepspaces=true,
	keywordstyle=\color{blue},
	morekeywords={*,...},
	escapeinside={(*}{*)}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray}, 
	rulecolor=\color{black},
	title=Proposed algorithm	
}

@@

\subsubsection{EasyMKL}
\label{EasyMKL}
EasyMKL \cite{Aiolli2015} is a recent MKL algorithm able to combine sets of basic kernels by solving a simple quadratic optimization problem. Besides its proved empirical effectiveness, a clear advantage of EasyMKL compared to other MKL methods is its high scalability with respect to the number of kernels to be combined. Specifically, its computational complexity is constant in memory and linear in time.
EasyMKL finds the coefficients $\boldsymbol{\eta}$ that maximize the margin on the training set, where the margin is computed as the distance between the convex hulls of positive and negative examples. In particular, the general problem EasyMKL tries to optimize is the following:
\vspace{-0.4cm}
\begin{equation}
\label{eq:easymklotig}
\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY \left( \sum_{r=0}^R \eta_r \KK_r\right) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2_2,
\end{equation}
%\vspace{-0.1cm}
where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\Lambda$ is a regularization hyperparameter. The domain $\Gamma$ represents two probability distributions over the set of positive and negative examples of the training set, that is $\Gamma = \{\boldsymbol{\gamma} \in \Real_+^{\ell} \hspace{0.2cm} |  \sum_{y_i = +1} \boldsymbol{\gamma}_i = 1 , \sum_{y_i = -1} \boldsymbol{\gamma}_i = 1\}.
$
Note that any element $\boldsymbol{\gamma} \in \Gamma$ corresponds to a pair of points, the first in the convex hull of positive training examples and the second in the convex hull of negative training examples.
At the solution, the first term of the objective function represents the obtained margin, that is the (squared) distance between a point in the convex hull of positive examples and a point in the convex hull of negative examples, in the compounded feature space.
%The objective function in Eq. \ref{eq:easymklotig} can be interpreted as the dual problem of a regularized empirical objective function using the kernel $\sum_{r=1}^R \eta_r \KK_r$.
Eq. \ref{eq:easymklotig} is a minimax problem that can be reduced  to a simple quadratic problem with a technical derivation described  in \cite{Aiolli2015}. %The solution of the quadratic problem is an optimal $\ggamma^*$ for the original min-max formulation. Due to the particular structure of EasyMKL, it is sufficient to provide the average kernel of all the basic kernels ($\KK^A = \frac{1}{R} \sum_{r=1}^R \frac{\KK_r}{Tr(\KK_r)}$). From $\ggamma^*$, it is easy to obtain the optimal weights for the single basic kernels $\KK_r$ by using the following formula
%\begin{equation}
%\label{eq:easyeta}
%	\eta_r = \gamma^{*T} \YY \,\, (\KK_r/Tr(\KK_r)) \,\, \YY \gamma^*, \,\,\,\, \forall r=1,\dots,R.
%\end{equation}
In the following sections, we will refer to this method as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
%and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyperparameter $\Lambda$.

@@

Firstly, we performed some experiments to check how many samples are required to make $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ similar.
In our context two weights vectors are similar if they provide the same top kernels. The metric used for comparison is the Jaccard similarity score. \figurename\ \ref{fig:jaccard} shows the Jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
According to preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%, except for MUTAG (the smallest datasets), where we use 20\% of training data.
%
%\begin{figure}[!htb]
\begin{figure}[t]
\centering
\includegraphics[width=0.42\textwidth]{img/CPDBh.png}
\includegraphics[width=0.42\textwidth]{img/GDDh.png}
\caption{Average jaccard values and standard deviation in 50 runs between the indices of top kernels using a subset of training data and using the whole set.}
\label{fig:jaccard}
\end{figure}
%
To learn $\hat{\boldsymbol{\eta}}$ we chose a random subsampling of training data and perform a 10-fold cross validation using EasyMKL to combine kernels and SVM as base learner. Then we fit the model with the best combination and select the top kernels.
In the second step we calculate the top kernel matrices using the whole training data and combine it to get the kernel. We propose 3 different methods to perform this combination:
(1)\ksmkl: using the EasyMKL algorithm, (2)\kssum: calculating the average of kernels, (3)\ksw: using the same weights (rescaled) from the first learning step.
In all of these methods we use a SVM as base learner. The hyper-parameters sets are the same used in baselines.\\
\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time used to make kernels and models for all problems.

%\begin{table}[]
%\centering
%\resizebox{\textwidth}{!}{
%\begin{tabular}{l|c|ccc|ccc}
%\hline\hline
%dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
%\hline
%MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{\tb{0.9331}}{0.053}    \\
%&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
%CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $\tb{0.8850}_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
%&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
%GDD     & 1178 & \res{0.8647}{0.045} & \res{\tb{0.8719}}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
%&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
%AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{\tb{0.7845}}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
%&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
%NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{\tb{0.8851}}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
%&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
%NCI109 & 4127 & \res{\tb{0.8728}}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
%&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
%CAS     & 4337 & \res{0.9189}{0.012} & - & \res{\tb{0.9209}}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
%&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
%\hline\hline
%\end{tabular}}
%\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
%\label{tab:res}
%\end{table}

\begin{table}[]
\centering
\resizebox{\textwidth}{!}{
\begin{tabular}{l|c|ccc|ccc}
\hline\hline
dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
\hline
MUTAG   & 188 & \res{0.90}{0.08} & \res{0.93}{0.06} & \res{0.93}{0.06} & \res{0.93}{0.05} & \res{0.93}{0.05} & \res{0.93}{0.05}    \\
&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
CPDB    & 684 & \res{0.88}{0.03} & \res{0.88}{0.03} & \res{0.88}{0.03} & \res{0.88}{0.02} & \res{0.89}{0.03} 	& \res{0.88}{0.02} \\
&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
GDD     & 1178 & \res{0.86}{0.05} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.80}{0.04}    \\
&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
AIDS    & 1503 & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.77}{0.07} & \res{0.77}{0.07}    \\
&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
NCI1    & 4110 & \res{0.88}{0.04} & - & \res{0.89}{0.04} & \res{0.88}{0.04} & \res{0.88}{0.05} & \res{0.88}{0.04}    \\
&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
NCI109 & 4127 & \res{0.87}{0.03} & - & \res{0.87}{0.03} & \res{0.87}{0.02}  & \res{0.87}{0.03} & \res{0.87}{0.02}  \\
&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
CAS     & 4337 & \res{0.92}{0.01} & - & \res{0.92}{0.01} & \res{0.92}{0.01} & \res{0.92}{0.01} & \res{0.92}{0.01}    \\
&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
\hline\hline
\end{tabular}}
\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
\label{tab:res}
\end{table}

@@

We have presented an efficient approach to model selection for graph kernels
based on the multiple kernel learning framework. We have shown how working on
small subsets (up to 10\%) of the data yields results that are stable and
accurate enough to select the optimal combination of kernels via EasyMKL.
We have investigated three methods to efficiently combine a subset of
kernels while preserving at the same time an high AUC score for the downstream
machine learning algorithms. Finally, we showed how we can use the simple
summation of the selected kernels, avoiding the expensive step of running MKL
on the full training set, to scale the MKL approach to very large
datasets.
In future work we will extend the library of graph kernels to obtain a
comprehensive and easy to use software package.

% ****************************************************************************
% BIBLIOGRAPHY AREA
% ****************************************************************************

\begin{footnotesize}

% IF YOU DO NOT USE BIBTEX, USE THE FOLLOWING SAMPLE SCHEME FOR THE REFERENCES
% ----------------------------------------------------------------------------

@@

% IF YOU USE BIBTEX,
% - DELETE THE TEXT BETWEEN THE TWO ABOVE DASHED LINES
% - UNCOMMENT THE NEXT TWO LINES AND REPLACE 'Name_Of_Your_BibFile'

\bibliographystyle{unsrt}
\bibliography{donini,biblio,Mendeley}

\end{footnotesize}

% ****************************************************************************
% END OF BIBLIOGRAPHY AREA
% ****************************************************************************

>>>>

\usepackage{listings}
\lstset{
	language=Python,
	basicstyle=\footnotesize,
	commentstyle=\color{mygreen},
	frame=single,
	keepspaces=true,
	keywordstyle=\color{blue},
	morekeywords={*,...},
	escapeinside={(*}{*)}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray}, 
	rulecolor=\color{black},
	%title=Proposed algorithm	
}

@@

\subsubsection{EasyMKL}
\label{EasyMKL}
EasyMKL \cite{Aiolli2015} is a recent MKL algorithm able to combine sets of basic kernels by solving a simple quadratic optimization problem. Besides its proved empirical effectiveness, a clear advantage of EasyMKL compared to other MKL methods is its high scalability with respect to the number of kernels to be combined. Specifically, its computational complexity is constant in memory and linear in time.
EasyMKL finds the coefficients $\boldsymbol{\eta}$ that maximize the margin on the training set, where the margin is computed as the distance between the convex hulls of positive and negative examples. In particular, the general problem EasyMKL tries to optimize is the following:
\vspace{-0.4cm}
\begin{equation}
\label{eq:easymklotig}
\max_{\boldsymbol{\eta}:||\boldsymbol{\eta}||_2=1} \min_{\boldsymbol{\gamma} \in \Gamma} \mbox { }  \boldsymbol{\gamma}^{\top} \YY \left( \sum_{r=0}^R \eta_r \KK_r\right) \YY \boldsymbol{\gamma} + \Lambda ||\boldsymbol{\gamma}||^2_2,
\end{equation}
%\vspace{-0.1cm}
where $\YY$ is a diagonal matrix with training labels on the diagonal, and $\Lambda$ is a regularization hyperparameter. The domain $\Gamma$ represents two probability distributions over the set of positive and negative examples of the training set, that is $\Gamma = \{\boldsymbol{\gamma} \in \Real_+^{\ell} \hspace{0.2cm} |  \sum_{y_i = +1} \boldsymbol{\gamma}_i = 1 , \sum_{y_i = -1} \boldsymbol{\gamma}_i = 1\}.
$
Note that any element $\boldsymbol{\gamma} \in \Gamma$ corresponds to a pair of points, the first in the convex hull of positive training examples and the second in the convex hull of negative training examples.
At the solution, the first term of the objective function represents the obtained margin, that is the (squared) distance between a point in the convex hull of positive examples and a point in the convex hull of negative examples, in the compounded feature space.
%The objective function in Eq. \ref{eq:easymklotig} can be interpreted as the dual problem of a regularized empirical objective function using the kernel $\sum_{r=1}^R \eta_r \KK_r$.
Eq. \ref{eq:easymklotig} is a minimax problem that can be reduced  to a simple quadratic problem with a technical derivation described  in \cite{Aiolli2015}. %The solution of the quadratic problem is an optimal $\ggamma^*$ for the original min-max formulation. Due to the particular structure of EasyMKL, it is sufficient to provide the average kernel of all the basic kernels ($\KK^A = \frac{1}{R} \sum_{r=1}^R \frac{\KK_r}{Tr(\KK_r)}$). From $\ggamma^*$, it is easy to obtain the optimal weights for the single basic kernels $\KK_r$ by using the following formula
%\begin{equation}
%\label{eq:easyeta}
%	\eta_r = \gamma^{*T} \YY \,\, (\KK_r/Tr(\KK_r)) \,\, \YY \gamma^*, \,\,\,\, \forall r=1,\dots,R.
%\end{equation}
In the following sections, we will refer to this method as EasyMKL\footnote{EasyMKL implementation: github.com/jmikko/EasyMKL}.
%and we have to provide it only $\KK^A$, the dataset $\XX$ and $\yy$ to evaluate equation \ref{eq:easyeta}, and the EasyMKL regularization hyperparameter $\Lambda$.

@@

Firstly, we performed some experiments to check how many samples are required to make $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ similar.
In our context two weights vectors are similar if they provide the same top kernels. The metric used for comparison is the Jaccard similarity score. \figurename\ \ref{fig:jaccard} shows the Jaccard score between the indices of top kernels selected using $\boldsymbol{\eta}$ and $\hat{\boldsymbol{\eta}}$ with different threshold and different subsampling dimension.
According to preliminary results, we fix the dimension of subset used in the first step to learn $\hat{\boldsymbol{\eta}}$ as 10\% and the number of top kernels as 10\%, except for MUTAG (the smallest datasets), where we use 20\% of training data.
%\begin{figure}[!htb]
\begin{figure}[t]
\centering
\includegraphics[width=0.42\textwidth]{img/CPDBh.png}
\includegraphics[width=0.42\textwidth]{img/GDDh.png}
\caption{Average jaccard values and standard deviation in 50 runs between the indices of top kernels using a subset of training data and using the whole set.}
\label{fig:jaccard}
\end{figure}
To learn $\hat{\boldsymbol{\eta}}$ we chose a random subsampling of training data and perform a 10-fold cross validation using EasyMKL to combine kernels and SVM as base learner. Then we fit the model with the best combination and select the top kernels.
In the second step we calculate the top kernel matrices using the whole training data and combine it to get the kernel. We propose 3 different methods to perform this combination:
(1)\ksmkl: using the EasyMKL algorithm, (2)\kssum: calculating the average of kernels, (3)\ksw: using the same weights (rescaled) from the first learning step.
In all of these methods we use a SVM as base learner. The hyper-parameters sets are the same used in baselines.
\tablename\ \ref{tab:res} shows the AUC score, standard deviation and computation time used to make kernels and models for all problems.
%\begin{table}[]
%\centering
%\resizebox{\textwidth}{!}{
%\begin{tabular}{l|c|ccc|ccc}
%\hline\hline
%dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
%\hline
%MUTAG   & 188 & \res{0.9023}{0.075} & \res{0.9310}{0.061} & \res{0.9309}{0.060} & \res{0.9292}{0.054} & \res{0.9292}{0.054} & \res{\tb{0.9331}}{0.053}    \\
%&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
%CPDB    & 684 &$0.8753_{\pm0.029}$ & $0.8814_{\pm0.027}$ & $0.8809_{\pm0.029}$ & $0.8768_{\pm0.023}$ & $\tb{0.8850}_{\pm0.027}$ & $0.8751_{\pm0.023}$ \\
%&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
%GDD     & 1178 & \res{0.8647}{0.045} & \res{\tb{0.8719}}{0.039} & \res{0.8675}{0.039} & \res{0.8690}{0.041} & \res{0.8713}{0.043} & \res{0.8011}{0.036}    \\
%&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
%AIDS    & 1503 & \res{0.7797}{0.083} & \res{0.7775}{0.080} & \res{0.7712}{0.083} & \res{\tb{0.7845}}{0.077} & \res{0.7690}{0.074} & \res{0.7673}{0.073}    \\
%&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
%NCI1    & 4110 & \res{0.8839}{0.043} & - & \res{\tb{0.8851}}{0.041} & \res{0.8818}{0.043} & \res{0.8772}{0.047} & \res{0.8811}{0.044}    \\
%&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
%NCI109 & 4127 & \res{\tb{0.8728}}{0.025} & - & \res{0.8713}{0.025} & \res{0.8670}{0.024}  & \res{0.8713}{0.025} & \res{0.8680}{0.022}  \\
%&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
%CAS     & 4337 & \res{0.9189}{0.012} & - & \res{\tb{0.9209}}{0.012} & \res{0.9195}{0.011} & \res{0.9161}{0.012} & \res{0.9185}{0.012}    \\
%&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
%\hline\hline
%\end{tabular}}
%\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
%\label{tab:res}
%\end{table}
\begin{table}[t]
\centering
\small
\resizebox{\textwidth}{!}{
\begin{tabular}{l|c|ccc|ccc}
\hline\hline
dataset & \# train &\kval &\kmkl &\ksum & \ksmkl & \kssum & \ksw \\
\hline
MUTAG   & 188 & \res{0.90}{0.08} & \res{0.93}{0.06} & \res{0.93}{0.06} & \res{0.93}{0.05} & \res{0.93}{0.05} & \res{0.93}{0.05}    \\
&			  & 18m					& 40m				& 8m		& 3m		&4m		&4m\\\hline
CPDB    & 684 & \res{0.88}{0.03} & \res{0.88}{0.03} & \res{0.88}{0.03} & \res{0.88}{0.02} & \res{0.89}{0.03} 	& \res{0.88}{0.02} \\
&			  & 1h 16m				& 8h 33m		& 20m	& 1h 37m		& 5m		&5m\\\hline
GDD     & 1178 & \res{0.86}{0.05} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.87}{0.04} & \res{0.80}{0.04}    \\
&			& $>$100h	& $>$100h	& $>$100h	&3h		& 4h 15m		& 4h 15m\\\hline
AIDS    & 1503 & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.78}{0.08} & \res{0.77}{0.07} & \res{0.77}{0.07}    \\
&		& 6h 39m		& 50h	& 2h 44m		& 11h 10m	& 1h 4m	& 1h 4m\\\hline
NCI1    & 4110 & \res{0.88}{0.04} & - & \res{0.89}{0.04} & \res{0.88}{0.04} & \res{0.88}{0.05} & \res{0.88}{0.04}    \\
&	&	39h	&-	& 7h 24m		& 98h	& 2h 1m	& 2h 1m\\\hline
NCI109 & 4127 & \res{0.87}{0.03} & - & \res{0.87}{0.03} & \res{0.87}{0.02}  & \res{0.87}{0.03} & \res{0.87}{0.02}  \\
&	&	44h	&-	& 7h 36m		& 99h	& 1h 47m	& 1h 47m\\\hline
CAS     & 4337 & \res{0.92}{0.01} & - & \res{0.92}{0.01} & \res{0.92}{0.01} & \res{0.92}{0.01} & \res{0.92}{0.01}    \\
&	&	38h	&-	& 4h 26m		&$>$100h	& 1h 34m		& 1h 34m\\	%176h
\hline\hline
\end{tabular}}
\caption{AUC score, standard deviation and computational time for all baselines and all subsampling proposed methods.}
\label{tab:res}
\end{table}

@@

We have presented an efficient approach to model selection for graph kernels
based on the multiple kernel learning framework. We have shown how working on
small subsets (up to 10\%) of the data yields results that are stable and
accurate enough to select the optimal combination of kernels via EasyMKL.
We have investigated three methods to efficiently combine a subset of
kernels while preserving at the same time an high AUC score for the downstream
machine learning algorithms. Finally, we showed how we can use the simple
summation of the selected kernels, avoiding the expensive step of running MKL
on the full training set, to scale the MKL approach to very large
datasets.
In future work we will extend the library of graph kernels to obtain a
comprehensive and easy to use software package.

% ****************************************************************************
% BIBLIOGRAPHY AREA
% ****************************************************************************
%
\begin{footnotesize}
%
% IF YOU DO NOT USE BIBTEX, USE THE FOLLOWING SAMPLE SCHEME FOR THE REFERENCES
% ----------------------------------------------------------------------------

@@

% IF YOU USE BIBTEX,
% - DELETE THE TEXT BETWEEN THE TWO ABOVE DASHED LINES
% - UNCOMMENT THE NEXT TWO LINES AND REPLACE 'Name_Of_Your_BibFile'
%
\bibliographystyle{unsrt}
\bibliography{donini,biblio,Mendeley}
%
\end{footnotesize}
%
% ****************************************************************************
% END OF BIBLIOGRAPHY AREA
% ****************************************************************************
